Rotation effects on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-04-29 paper/Analisis.tex

As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}. For the central distribution the number of scattering does not change with $V_{max}$ , this implies that..., For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation..

In order to understand the double peack we make a histogram..

@@

\begin{figure*}[ht]
    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
\caption{Nscatt\label{fig:Nscatt}} 
\end{figure*}

\begin{figure*}[ht]
    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
\caption{Nscatt\label{fig:NscattHisto}} 
\end{figure*}

>>>>

As a first approach we study the number of scatterings of all the photons at different velocites and for both distributions Figure~\ref{fig:Nscatt}. For the central distribution we found that the average number of scattering does not have a relevant change (put the exact value) with $V_{max}$, For the Homogeneous distribution we found that as $V_{max}$ increase the average number of scatterings decrease, it means that rotation make photons to escape easier from the cloud, and the reason why this is not observed in the central distribution. it is because the amount of gas that every photon has to break through is so large an so the average number of scatterings, making the effect of rotation unobservable.

In order to understand the morphology of the line we make a histogram of $<N_{scatt}>$  in function of $X_{m}$

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
\caption{Nscatt\label{fig:Nscatt}} 
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{2dHistogram50Central5t.png}
    \includegraphics[width=0.45\textwidth]{2dHistogram300Central5t.png}
\caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the central distribution\label{fig:NscattHisto}} 
\end{figure*}

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{2dHistogramt5HOM.png}
    \caption{Histogram of $N_{scatt}$ vs $X_{m}$ for the homogeneous distribution\label{fig:NscattHistoHOM}} 
\end{figure*}
